|

### 2020-05-19 paper/Manuscript.Rmd
Rewrite paragraph about existing approaches

## Goal of this paper

The TOP-guidelines are primarily geared towards top-down systemic change (what's in a name) by journals, funders, and organizations.
However, large organizations are slow to change.
For example, a snapshot of editorial practices indicated that, in 2015, only 3% out of 1151 psychology journals explicitly stated that
they accepted replication studies [@martinArePsychologyJournals2017; see also @klebelPeerReviewPreprint2020].
At the same time, <!-- edit -->
The formation of "Open Science Communities" at universities around the globe
illustrates the momentum of this grassroots movement
[@brinkmanWidescaleAdoptionOpen2020].

@@

A different class of solutions instead focuses on the practical issue of *how* researchers can meet the requirements of open science. <!--limitation of signalling approaches, that WORCS addresses, is that they do not clarify One could use WORCS to meet the TOP-guidelines, and document this in a TOP-statement.--> One notable example is the workflow for reproducible analyses developed by @peikertReproducibleDataAnalysis2019. Because that workflow focuses on computational reproducibility, it only addresses TOP-guidelines 2, 3, and 5. Moreover, in striving to ensure strict computational reproducibility for even the most sophisticated analyses, Peikert and Brandmaier's workflow ends up being relatively complex to implement. WORCS is designed to be a simple and sufficient solution for projects that can be conducted entirely within R. It eschews much overhead of Peikert and Brandmaier's workflow, resulting in a much more lightweight approach to safeguard computational reproducibility under *most circumstances*. Importantly, WORCS builds upon the same general principles as Peikert and Brandmaier, which means the two workflows are compatible. Finally, WORCS addresses a unique issue not covered by other existing solutions, namely to provide a workflow most conducive to satisfying the TOP-guidelines, while being compatible with existing approaches.

>>>>

<!--## Goal of this paper

The TOP-guidelines are primarily geared towards top-down systemic change (what's in a name) by journals, funders, and organizations.
However, large organizations are slow to change.
For example, a snapshot of editorial practices indicated that, in 2015, only 3% out of 1151 psychology journals explicitly stated that
they accepted replication studies [@martinArePsychologyJournals2017; see also @klebelPeerReviewPreprint2020].
At the same time, <!-- edit -->
<!--The formation of "Open Science Communities" at universities around the globe
illustrates the momentum of this grassroots movement
[@brinkmanWidescaleAdoptionOpen2020]. -->

@@

A different class of solutions instead focuses on the practical issue of *how*
researchers can meet the requirements of open science. <!--limitation of signalling approaches, that WORCS addresses, is that they do not clarify One could use WORCS to meet the TOP-guidelines, and document this in a TOP-statement.--> One notable example is the workflow for
reproducible analyses developed by @peikertReproducibleDataAnalysis2019. This 
excellent workflow strives to ensure strict computational reproducibility for
even the most sophisticated analyses. It has some limitations, however: In
focusing on reproducibility, however, it only addresses TOP-guidelines 2, 3, and
5. Moreover, in aiming for strict computational reproducibility it ends up being
relatively complex to implement. WORCS builds upon the same general principles
as Peikert and Brandmaier, which means the two workflows are compatible. What 
sets WORCS apart is that is an easy and sufficient solution for projects that
can be conducted entirely within R, resulting in a much more lightweight
approach to safeguard computational reproducibility under *most circumstances*.
WORCS also addresses a unique issue not covered by other existing solutions,
namely to provide a workflow most conducive to satisfying the TOP-guidelines and
FAIR principles, while being compatible with existing requirements.
